\plaintitle

### 2016-09-12 drafts/labor/cases.tex
piecework_lit should be kind of done

We look at lots of papers that use the term ``crowdsourcing'' or ``crowdwork''
in the abstracts and titles of their papers,
especially the papers that we cited earlier, to try
to answer the questions that we posed in the introduction.
Then we look to the piecework literature to see whether and to what extent
piecework answers the questions we, crowdsourcing researchers, have asked.
We then see whether and how crowdsourcing as we know it has differed from piecework,
and how that affects the predictions and conclusions made in the piecework literature.
% look at review papers

@@

\subsection{What are the limits of crowdsourcing?}
\topic{Research in crowdsourcing has spent the better part of a decade
exploring how to grow the limits of crowdsourcing and
find the boundaries of crowd work and microtasks.}
This has largely involved
  identifying challenges to this form of labor,
  overcoming them through novel designs of work--flows and processes, and
  repeating the process
\cite[e.g.][]{bernsteinSoylent,foundry,crowdForgeKittur}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been driving at \textit{whether} there are limits to crowdsourcing
(and, if so, what factors determine those limits).
Through this lens, we can point to
a number of contributions to the field that have extended the boundaries of crowd work.

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  \item \nameref{sec:complexity},
  \item \nameref{sec:decomposition}, and
  \item \nameref{sec:relationships}
\end{inlinelist}.
We'll explore these aspects of crowdsourcing,
discussing the extents to which work can be
decomposed,
contextually abstracted, and
made more resilient to attrition of various forms.
We'll also point to corresponding piecework literature addressing these aspects.
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

\subfile{complexity}
\subfile{slicing}
\subfile{flexibility}

\endnotetext{
Here, \citeauthor{hu1961parallel}'s work,
saying of assembly line work that
``it is assumed that men are of equal ability and every man can do any of the $n$ jobs'',
parallels the approach that dominated early research into crowd work
--- namely, using non--expert crowds for complex work
\cite{hu1961parallel}.
This mindset in \citeauthor{hu1961parallel}'s analysis,
and indeed the study of factory and mass manufacturing labor through the \nth{20} century,
substantively owes its existence to scientific management
and the rigorous decomposition of work into tasks, discussed earlier,
and persists to this day as it colors
researchers' goals and objectives in the study and design of crowd work.

Piecework's influence on the abstraction of work into tasks,
described above, is more than just caused by the decomposition of work;
work abstraction itself makes it possible for workers to come and go flexibly,
prompting work requesters to consider ways to design these now discrete tasks in ways that
maximize flexibility, both by allowing (and even anticipating) some inconsistency in worker availability
\textit{and} allowing and anticipating some inconsistency in the quality of the work output itself.
It's to this area that we now turn our attention.

@@

Piecework has seen work along this dimension spanning decades;
\citeauthor{thompson1913time} investigate some of the ways that
construction can benefit from the principles of scientific management.
\citeauthor{thompson1913time}'s thesis asserts that
task work is predicated on the accurate scientific management of work,
including the ``miscellaneous tasks''.
\citeauthor{thompson1913time} argues
--- as early as \citeyear{thompson1913time} ---
that ``\dots one may be challenged to find any class of work
involving labor either indoors or out--of--doors
where tasks cannot be fixed by proper time--study''
\cite{thompson1913time}.

Broken down in this way, work could grow to unprecedented scales,
but the quality of the work would remain relatively variable
\cite{murray1983decentralisation}.
Textile work being a salient example,
it took time for workers to acquire sufficient skill
to do every aspect of the work so that the garment would be accepted by the company soliciting that work
\cite{vezina1992light}.

A compelling solution emerged in the early \nth{20} century to break tasks down into discrete,
manageable routines that could be taught relatively easily,
and whose work output could be evaluated in abstraction from the rest of the work
\cite{restructuringPieceworkBaker}.
In Ford's assembly line, this meant that workers were not responsible for building a whole car,
but a single very narrowly defined action that needed to be done on every car
\cite{towardsGlobalFordism}.
By the mid--\nth{20} century, \citeauthor{schoenberger1988fordism} writes,
``\dots~the intensification of the labor process is argued to have hit mental, physical, and social limits.''
\cite{schoenberger1988fordism}.

This approach, ``Fordism'' (and its better--known contemporary ``Taylorism'' of similar ethos),
can be seen today in crowd work and on--demand labor through the application of micro--tasks.
\citeauthor{writingMicroTasks} highlight some of the advantages of breaking work into pieces,
facilitating evaluation and parallelization
\cite{writingMicroTasks}.
By decomposing and recomposing tasks,
and in particular by assigning similarly natured work to the same workers,
workers could become ``experts'' in a small aspect of the work that they did,
speeding their work dramatically
\cite{delayAndOrderLasecki}.
Perhaps more important, however, was that
the breaking down of work into tasks has made it more practical to evaluate work at each stage
\cite{rogstadius2011assessment}.

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
  % \nobalance{}
  \clearpage
  \nobalance{}
  }
  % \begin{appendices}
% \section{Graveyard}
\endnotetext{
\section{Cases notes}
    \citeauthor{cheng2015break} found that microtasks
    --- though not necessarily \textit{faster} than ``macrotasks'' ---
    yield higher quality work,
    particularly when that work is susceptible to frequent interruptions
    \cite{cheng2015break}.
  % }
  % \endnotetext{
  \subsection{What forms of work design and worker management are viable?}
  \begin{itemize}
    \item researchers have looked at how to increase worker productivity
    (e.g. finding the maximal speed at which gig workers can be expected to work before making errors)
    \cite{measuringCrowdsourcingCheng}.
    \item we've also seen people ``embrace error''
    \cite{embracingErrorKrishna}.
    \item still other research has looked into ways to sandbox workers from the context of their work 
    \item but scholarship looking into the design and management of work and workers isn't new;
    lots of research into getting pieceworkers to do work more quickly
    \cite{seymour1954manual}.
    \item Researchers have even asked the age old question of \textit{what motivates} pieceworkers
    (echoing similar research on Wikipedia and Mechanical Turk)
    \cite{roy1953work,Nov:2007:MW:1297797.1297798,kaufmann2011more}
  \end{itemize}

  \subsection{What will work and the place of work look like for workers?}
  The metaphorical mechanics of these dynamics are still at play;
  workers and managers continue to interact in adversarial manners,
  despite substantive work into aligning the motivations of workers and requesters

    % \section{Case Studies}
    The existing body of research has shed light on on--demand labor from various perspectives,
    and revealed a number of topics that,
    through our framing, are clearly situated together.
    Those topics are, at a high level, as follows:
    \begin{enumerate}
    \item the \textbf{processes} involved in making work into tasks, or discretization;
    \item the outcomes (and indeed the \textbf{fallout}) of that discretization,
    both on the work itself as well as the workers;
    and finally
    \item the \textbf{relationships} between workers and requesters of the work
    --- both \textit{cooperative} and \textit{adversarial} cases.
    \end{enumerate}

    \subsection{The Fallout of Crowd Work}
    % If the research exploring and documenting how we can exploit crowd \textit{work} can be described as wide--ranging,
    % the scholarship discussing the ways crowd \textit{workers} have been exploited is more focused;
    \citeauthor{turkopticon} point out the disillusion that companies such as Amazon foster on platforms for work like AMT
    (see also \citeauthor{dynamo}'s work
    continuing in the spirit of this observation to generate collective action to improve worker conditions)
    \cite{turkopticon,dynamo}.
    \citeauthor{uberAlgorithm}
    find similarly that workers on gig work platforms are frustrated by the systems on which they work,
    to say little of the policies which these systems enforce
    \cite{uberAlgorithm}.

@@

    \citeauthor{laborEconomicsOfCrowdsourcingHorton}
    identified problems with crowd work wages relatively early on,
    attempting to address this imbalance from a behavioral economic perspective ---
    that is, identifying and presenting a model that describes a worker's
    ``\textit{reservation wage}''
    \cite{laborEconomicsOfCrowdsourcingHorton}.
    This work has largely informed much of the research into and practice of estimating crowd work compensation
    \cite{incentivesShaw,paolacci2010running}.

    But we turn to \citeauthor{turkopticon}'s discussion of ``\textit{Turkopticon}'',
    a system they designed to interrogate worker invisibility and to promote better wages across several dimensions
    \cite{turkopticon}.
    Of particular relevance here,
    \citeauthor{turkopticon} call to attention that ``Turkers'' are ultimately vulnerable to
    wage theft and
    pay rates that translate to well under minimum wage.
    Returning to \citeauthor{laborEconomicsOfCrowdsourcingHorton},
    we find that the median ``reservation wage'' in \citeyear{laborEconomicsOfCrowdsourcingHorton}
    was \$1.38, while the mean was \$3.63
    \cite{laborEconomicsOfCrowdsourcingHorton}.

    Understanding workers' motivations given these conditions has thus become a goal for some researchers
    \cite{whyWouldAnyoneBrewer}.
    \citeauthor{Sun20111033} conclude that
    ``\dots~solvers participate in online tasks
    not only for money
    but also for enjoyment
    or the sense of self--worth''
    \cite{Sun20111033}.
    This might have rung true in \citeyear{Sun20111033},
    and certainly corroborates \citeauthor{Ross}'s findings after investigating
    ``who are the crowdworkers'',
    but as \citeauthor{whoareNOTtheTurkers} points out
    ``we [have since] learned that most tasks on AMT are done by a small group of professional Turkers\dots''
    \cite{Ross,whoareNOTtheTurkers}.

    Now, \citeauthor{turkopticon}
    and later
    \citeauthor{dynamo} cite insufficient pay as a central point of frustration among workers,
    via \citeauthor{irani2015cultural} and \citeauthor{dawnDigitalSweatshopCushing}'s contributions in this space
    \cite{dynamo,irani2015cultural,dawnDigitalSweatshopCushing,turkopticon}.

    On--demand workers were not the first to be exploited along the dimension of low pay rates.
    Frustration over low (and declining) pay was one of the chief grievances among then nascent
    British labor unions in the early \nth{20} century
    \cite{turner1952trade}.
    This, \citeauthor{ebbinghaus1999institutions} argued,
    fueled the rocketing union membership rates through the mid--\nth{20} century until 1980
    (to which we'll return when we discuss \citeauthor{levi2009union}'s reexamination of labor unions)
    \cite{ebbinghaus1999institutions,levi2009union}.
    This realization has similarly fueled a body of research into
    the various incentive structures available to piecework employers
    \cite{roy1953work}.

    The parallels between the complaints of low pay among crowd workers and other on--demand workers
    and the pieceworkers and later factory workers in the \nth{20} century
    are inescapable.
    We argue further that the \textit{causes} here
    --- work decomposition,
    work abstraction, and
    flexibility ---
    lead inexorably to low and declining pay for workers.
    Moreover, we point out that low pay leads to other negative outcomes both
    in on--demand work
    as well as
    in piecework and on assembly lines.

    \subsubsection{Variable quality work}
    Researchers have struggled with what we might generously call work of ``variable quality''
    along two dimensions.
    The first, to use the characterization of one of these contributions, we can call
    ``understanding malicious behavior''
    \cite{MaliciousCrowdworkersGadiraju}.
    While some work has cast workers as ``malicious'' or at least adversarial parties,
    the evidence thus far suggests that
    workers behave in unexpected ways as they attempt to assert some control over their interaction with the system
    (a topic of discussion to which we'll return later)
    \cite{uberAlgorithm}.
    The second dimension of research in this space generally attempts
    to eke out the highest quality work possible from workers
    given the apparent difficulty in predicting work outcomes
    \cite{embracingErrorKrishna}.

@@

    This research is similar to, but subtly different from, the notion of the ``market for `lemons'''
    which \citeauthor{fort2011amazon} discuss;
    specifically, \citeauthor{akerlof1970market}'s writing of a ``market for `lemons'''
    describes a marketplace where the quality of the product or service is unknown to the buyer
    \cite{fort2011amazon,akerlof1970market}.
    The effect of this \textit{perceived} uncertainty is that
    the \textit{actual} trustworthiness drops precipitously
    as all of the consistent, reliable, high--quality workers capable of leaving these markets do so,
    leaving only the ones who cannot or will not establish their trustworthiness.

    \subsection{Relationships Between Workers and Managers}
    Suffice it to say that poor pay and poor work are linked,
    and that we should not be surprised to find this relationship play out online as strongly as it does offline.
    But the poor treatment of workers by managers
    --- both human and algorithmic ---
    do more than affect the economic relationships between workers and employers.
    Here, then, we turn to examine this facet of on--demand work
    and how these dynamics strikingly replicate the relationships
    researchers in labor advocacy encountered in the study of piecework and factory work.

@@

    \subsubsection{External Management}
    We discussed Fordism and Taylorism earlier in our discussions of
    \nameref{sec:Complexity} and \nameref{sec:flexibility},
    but here the core of these paradigmatic views
    --- the scientific management of work ---
    becomes relevant.
    We use ``external'' here instead of ``scientific'', however,
    to more broadly capture the disconnect between managers and workers.
    By describing it as thus,
    we can touch on the relationship that workers have with \textit{researchers}, as well,
    even though that work is not strictly
    --- or just not exclusively ---
    of the same nature as the management and experience as when interacting with requesters.

    First, intuitively, the variable--quality work we discussed previously has led to
    a large and growing body of research attempting to evaluate workers' performance and error rates
    across numerous dimensions;
    for example, \citeauthor{measuringCrowdsourcingCheng} explore the error rates of workers by
    operating on a sliding scale giving workers varying amounts of time to accomplish micro--tasks
    \cite{measuringCrowdsourcingCheng}.
    \citeauthor{storiesIraniSilberman} describe the treatment of workers
    as sorts of ``human APIs'' that can, importantly, be rigorously evaluated
    \cite{storiesIraniSilberman}.
    \citeauthor{gevins2003neurophysiological} began to explore the neurophysiological effects of
    cognitively demanding tasks on workers,
    informing crowdsourcing research by suggesting the use of cognitive load assessments such as
    NASA Task Load Index surveys to evaluate workers pre and post--tasks
    \cite{embracingErrorKrishna,measuringCrowdsourcingCheng}.

    External management comes in other forms than scientific, as previously mentioned.
    Researchers in particular have noticed that their relationships with on--demand workers are,
    at the least, complex.
    \citeauthor{storiesIraniSilberman} point out that their relationships with Turkers are highly complex;
    specifically, their interactions with field sites in which they work
    as designers and mediators of change influence the relationships they have with Turkers
    \cite{storiesIraniSilberman}.

    The scientific management of pieceworkers has been well--studied under the umbrella of assembly line research,
    and even physiological study of pieceworkers closely resembles the
    research into cognitive loads and stress levels that we discussed among on--demand crowd workers
    \cite{hu1961parallel,pieceworkBiologicalHarm}.
    Even the complicated relationships between observers and workers themselves are not necessarily new;
    \citeauthor{riisOtherSideLives}'s photodocumentary of pieceworkers has even been re--examined through an exercise asking crowd workers
    to photograph themselves for similar purposes as \citeauthor{riisOtherSideLives}'s --- to document and humanize an otherwise abstracted, invisible workforce
    \cite{facesOfMechanicalTurk,turkopticon,riisOtherSideLives}.

@@

    \subsubsection{Resistance}
    It shouldn't surprise us, then, that workers have resisted the management imposed on them both by other people and their systems,
    often without recourse or opportunity for feedback, let alone substantive input.
    Indeed, \citeauthor{uberAlgorithm} discover of Uber drivers that 
    many toggle their availability to avoid being dispatched to more distant locations,
    resisting the intent of the designers of the systems and their ``algorithmic and data--driven management''
    \cite{uberAlgorithm}.

@@

    Resistance against managers in piecework and factory labor settings are deeply well--explored,
    but perhaps the most relevant case study to draw on here is to be found in
    \citeauthor{waldinger1996helots}'s case study of ``Justice for Janitors'',
    where marginalized workers managed to raise awareness for their plight and secure support for badly needed reforms
    \cite{waldinger1996helots}.
    The achievements of labor advocacy groups such as labor unions as resistant,
    even adversarial organizations counter--balancing the management
    is somewhat well--understood
    \cite{russell1982collective,craig1992behavior}.
    We argue that these threads of resistance against management in various forms
    are in fact one.
  }
  % \theendnotes
  % \end{appendices}

>>>>

We look at lots of papers that use the term ``crowdsourcing'' or ``crowdwork''
in the abstracts and titles of their papers%
, especially the papers that we cited earlier, to try
to answer the questions that we posed in the introduction.
Then we look to the piecework literature to see whether and to what extent
piecework answers the questions we, crowdsourcing researchers, have asked.
We then see whether and how crowdsourcing as we know it has differed from piecework%
, and how that affects the predictions and conclusions made in the piecework literature.
% look at review papers

@@

\subsection{What are the limits of crowdsourcing?}
\topic{Research in crowdsourcing has spent the better part of a decade
exploring how to grow the limits of crowdsourcing and
find the boundaries of crowd work and microtasks.}
This has largely involved
  identifying challenges to this form of labor%
,   overcoming them through novel designs of work--flows and processes, and
  repeating the process
\cite[e.g.][]{bernsteinSoylent,foundry,crowdForgeKittur}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been driving at \textit{whether} there are limits to crowdsourcing
(and, if so, what factors determine those limits).
Through this lens, we can point to
a number of contributions to the field that have extended the boundaries of crowd work.

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  \item \nameref{sec:complexity}%
,   \item \nameref{sec:decomposition}, and
  \item \nameref{sec:relationships}
\end{inlinelist}.
We'll explore these aspects of crowdsourcing%
, discussing the extents to which work can be
decomposed%
, contextually abstracted, and
made more resilient to attrition of various forms.
We'll also point to corresponding piecework literature addressing these aspects.
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

\subfile{complexity.tex}
\subfile{decomposition.tex}
\subfile{relationships.tex}

\endnotetext{
Here, \citeauthor{hu1961parallel}'s work%
, saying of assembly line work that
``it is assumed that men are of equal ability and every man can do any of the $n$ jobs''%
, parallels the approach that dominated early research into crowd work
--- namely, using non--expert crowds for complex work
\cite{hu1961parallel}.
This mindset in \citeauthor{hu1961parallel}'s analysis%
, and indeed the study of factory and mass manufacturing labor through the \nth{20} century%
, substantively owes its existence to scientific management
and the rigorous decomposition of work into tasks, discussed earlier%
, and persists to this day as it colors
researchers' goals and objectives in the study and design of crowd work.

Piecework's influence on the abstraction of work into tasks%
, described above, is more than just caused by the decomposition of work;
work abstraction itself makes it possible for workers to come and go flexibly%
, prompting work requesters to consider ways to design these now discrete tasks in ways that
maximize flexibility, both by allowing (and even anticipating) some inconsistency in worker availability
\textit{and} allowing and anticipating some inconsistency in the quality of the work output itself.
It's to this area that we now turn our attention.

@@

Piecework has seen work along this dimension spanning decades;
\citeauthor{thompson1913time} investigate some of the ways that
construction can benefit from the principles of scientific management.
\citeauthor{thompson1913time}'s thesis asserts that
task work is predicated on the accurate scientific management of work%
, including the ``miscellaneous tasks''.
\citeauthor{thompson1913time} argues
--- as early as \citeyear{thompson1913time} ---
that ``\dots one may be challenged to find any class of work
involving labor either indoors or out--of--doors
where tasks cannot be fixed by proper time--study''
\cite{thompson1913time}.

Broken down in this way, work could grow to unprecedented scales%
, but the quality of the work would remain relatively variable
\cite{murray1983decentralisation}.
Textile work being a salient example%
, it took time for workers to acquire sufficient skill
to do every aspect of the work so that the garment would be accepted by the company soliciting that work
\cite{vezina1992light}.

A compelling solution emerged in the early \nth{20} century to break tasks down into discrete%
, manageable routines that could be taught relatively easily%
, and whose work output could be evaluated in abstraction from the rest of the work
\cite{restructuringPieceworkBaker}.
In Ford's assembly line, this meant that workers were not responsible for building a whole car%
, but a single very narrowly defined action that needed to be done on every car
\cite{towardsGlobalFordism}.
By the mid--\nth{20} century, \citeauthor{schoenberger1988fordism} writes%
, ``\dots~the intensification of the labor process is argued to have hit mental, physical, and social limits.''
\cite{schoenberger1988fordism}.

This approach, ``Fordism'' (and its better--known contemporary ``Taylorism'' of similar ethos)%
, can be seen today in crowd work and on--demand labor through the application of micro--tasks.
\citeauthor{writingMicroTasks} highlight some of the advantages of breaking work into pieces%
, facilitating evaluation and parallelization
\cite{writingMicroTasks}.
By decomposing and recomposing tasks%
, and in particular by assigning similarly natured work to the same workers%
, workers could become ``experts'' in a small aspect of the work that they did%
, speeding their work dramatically
\cite{delayAndOrderLasecki}.
Perhaps more important, however, was that
the breaking down of work into tasks has made it more practical to evaluate work at each stage
\cite{rogstadius2011assessment}.

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
  % \nobalance{}
  % \clearpage
  \nobalance{}
  }
  % \begin{appendices}
% \section{Graveyard}
\endnotetext{
\section{Cases notes}
    \citeauthor{cheng2015break} found that microtasks
    --- though not necessarily \textit{faster} than ``macrotasks'' ---
    yield higher quality work%
,     particularly when that work is susceptible to frequent interruptions
    \cite{cheng2015break}.
  % }
  % \endnotetext{
  \subsection{What forms of work design and worker management are viable?}
  \begin{itemize}
    \item researchers have looked at how to increase worker productivity
    (e.g. finding the maximal speed at which gig workers can be expected to work before making errors)
    \cite{measuringCrowdsourcingCheng}.
    \item we've also seen people ``embrace error''
    \cite{embracingErrorKrishna}.
    \item still other research has looked into ways to sandbox workers from the context of their work 
    \item but scholarship looking into the design and management of work and workers isn't new;
    lots of research into getting pieceworkers to do work more quickly
    \cite{seymour1954manual}.
    \item Researchers have even asked the age old question of \textit{what motivates} pieceworkers
    (echoing similar research on Wikipedia and Mechanical Turk)
    \cite{roy1953work,Nov:2007:MW:1297797.1297798,kaufmann2011more}
  \end{itemize}

  \subsection{What will work and the place of work look like for workers?}
  The metaphorical mechanics of these dynamics are still at play;
  workers and managers continue to interact in adversarial manners%
,   despite substantive work into aligning the motivations of workers and requesters

    % \section{Case Studies}
    The existing body of research has shed light on on--demand labor from various perspectives%
,     and revealed a number of topics that%
,     through our framing, are clearly situated together.
    Those topics are, at a high level, as follows:
    \begin{enumerate}
    \item the \textbf{processes} involved in making work into tasks, or discretization;
    \item the outcomes (and indeed the \textbf{fallout}) of that discretization%
,     both on the work itself as well as the workers;
    and finally
    \item the \textbf{relationships} between workers and requesters of the work
    --- both \textit{cooperative} and \textit{adversarial} cases.
    \end{enumerate}

    \subsection{The Fallout of Crowd Work}
    % If the research exploring and documenting how we can exploit crowd \textit{work} can be described as wide--ranging%
,     % the scholarship discussing the ways crowd \textit{workers} have been exploited is more focused;
    \citeauthor{turkopticon} point out the disillusion that companies such as Amazon foster on platforms for work like AMT
    (see also \citeauthor{dynamo}'s work
    continuing in the spirit of this observation to generate collective action to improve worker conditions)
    \cite{turkopticon,dynamo}.
    \citeauthor{uberAlgorithm}
    find similarly that workers on gig work platforms are frustrated by the systems on which they work%
,     to say little of the policies which these systems enforce
    \cite{uberAlgorithm}.

@@

    \citeauthor{laborEconomicsOfCrowdsourcingHorton}
    identified problems with crowd work wages relatively early on%
,     attempting to address this imbalance from a behavioral economic perspective ---
    that is, identifying and presenting a model that describes a worker's
    ``\textit{reservation wage}''
    \cite{laborEconomicsOfCrowdsourcingHorton}.
    This work has largely informed much of the research into and practice of estimating crowd work compensation
    \cite{incentivesShaw,paolacci2010running}.

    But we turn to \citeauthor{turkopticon}'s discussion of ``\textit{Turkopticon}''%
,     a system they designed to interrogate worker invisibility and to promote better wages across several dimensions
    \cite{turkopticon}.
    Of particular relevance here%
,     \citeauthor{turkopticon} call to attention that ``Turkers'' are ultimately vulnerable to
    wage theft and
    pay rates that translate to well under minimum wage.
    Returning to \citeauthor{laborEconomicsOfCrowdsourcingHorton}%
,     we find that the median ``reservation wage'' in \citeyear{laborEconomicsOfCrowdsourcingHorton}
    was \$1.38, while the mean was \$3.63
    \cite{laborEconomicsOfCrowdsourcingHorton}.

    Understanding workers' motivations given these conditions has thus become a goal for some researchers
    \cite{whyWouldAnyoneBrewer}.
    \citeauthor{Sun20111033} conclude that
    ``\dots~solvers participate in online tasks
    not only for money
    but also for enjoyment
    or the sense of self--worth''
    \cite{Sun20111033}.
    This might have rung true in \citeyear{Sun20111033}%
,     and certainly corroborates \citeauthor{Ross}'s findings after investigating
    ``who are the crowdworkers''%
,     but as \citeauthor{whoareNOTtheTurkers} points out
    ``we [have since] learned that most tasks on AMT are done by a small group of professional Turkers\dots''
    \cite{Ross,whoareNOTtheTurkers}.

    Now, \citeauthor{turkopticon}
    and later
    \citeauthor{dynamo} cite insufficient pay as a central point of frustration among workers%
,     via \citeauthor{irani2015cultural} and \citeauthor{dawnDigitalSweatshopCushing}'s contributions in this space
    \cite{dynamo,irani2015cultural,dawnDigitalSweatshopCushing,turkopticon}.

    On--demand workers were not the first to be exploited along the dimension of low pay rates.
    Frustration over low (and declining) pay was one of the chief grievances among then nascent
    British labor unions in the early \nth{20} century
    \cite{turner1952trade}.
    This, \citeauthor{ebbinghaus1999institutions} argued%
,     fueled the rocketing union membership rates through the mid--\nth{20} century until 1980
    (to which we'll return when we discuss \citeauthor{levi2009union}'s reexamination of labor unions)
    \cite{ebbinghaus1999institutions,levi2009union}.
    This realization has similarly fueled a body of research into
    the various incentive structures available to piecework employers
    \cite{roy1953work}.

    The parallels between the complaints of low pay among crowd workers and other on--demand workers
    and the pieceworkers and later factory workers in the \nth{20} century
    are inescapable.
    We argue further that the \textit{causes} here
    --- work decomposition%
,     work abstraction, and
    flexibility ---
    lead inexorably to low and declining pay for workers.
    Moreover, we point out that low pay leads to other negative outcomes both
    in on--demand work
    as well as
    in piecework and on assembly lines.

    \subsubsection{Variable quality work}
    Researchers have struggled with what we might generously call work of ``variable quality''
    along two dimensions.
    The first, to use the characterization of one of these contributions, we can call
    ``understanding malicious behavior''
    \cite{MaliciousCrowdworkersGadiraju}.
    While some work has cast workers as ``malicious'' or at least adversarial parties%
,     the evidence thus far suggests that
    workers behave in unexpected ways as they attempt to assert some control over their interaction with the system
    (a topic of discussion to which we'll return later)
    \cite{uberAlgorithm}.
    The second dimension of research in this space generally attempts
    to eke out the highest quality work possible from workers
    given the apparent difficulty in predicting work outcomes
    \cite{embracingErrorKrishna}.

@@

    This research is similar to, but subtly different from, the notion of the ``market for `lemons'''
    which \citeauthor{fort2011amazon} discuss;
    specifically, \citeauthor{akerlof1970market}'s writing of a ``market for `lemons'''
    describes a marketplace where the quality of the product or service is unknown to the buyer
    \cite{fort2011amazon,akerlof1970market}.
    The effect of this \textit{perceived} uncertainty is that
    the \textit{actual} trustworthiness drops precipitously
    as all of the consistent, reliable, high--quality workers capable of leaving these markets do so%
,     leaving only the ones who cannot or will not establish their trustworthiness.

    \subsection{Relationships Between Workers and Managers}
    Suffice it to say that poor pay and poor work are linked%
,     and that we should not be surprised to find this relationship play out online as strongly as it does offline.
    But the poor treatment of workers by managers
    --- both human and algorithmic ---
    do more than affect the economic relationships between workers and employers.
    Here, then, we turn to examine this facet of on--demand work
    and how these dynamics strikingly replicate the relationships
    researchers in labor advocacy encountered in the study of piecework and factory work.

@@

    \subsubsection{External Management}
    We discussed Fordism and Taylorism earlier in our discussions of
    \nameref{sec:Complexity} and \nameref{sec:flexibility}%
,     but here the core of these paradigmatic views
    --- the scientific management of work ---
    becomes relevant.
    We use ``external'' here instead of ``scientific'', however%
,     to more broadly capture the disconnect between managers and workers.
    By describing it as thus%
,     we can touch on the relationship that workers have with \textit{researchers}, as well%
,     even though that work is not strictly
    --- or just not exclusively ---
    of the same nature as the management and experience as when interacting with requesters.

    First, intuitively, the variable--quality work we discussed previously has led to
    a large and growing body of research attempting to evaluate workers' performance and error rates
    across numerous dimensions;
    for example, \citeauthor{measuringCrowdsourcingCheng} explore the error rates of workers by
    operating on a sliding scale giving workers varying amounts of time to accomplish micro--tasks
    \cite{measuringCrowdsourcingCheng}.
    \citeauthor{storiesIraniSilberman} describe the treatment of workers
    as sorts of ``human APIs'' that can, importantly, be rigorously evaluated
    \cite{storiesIraniSilberman}.
    \citeauthor{gevins2003neurophysiological} began to explore the neurophysiological effects of
    cognitively demanding tasks on workers%
,     informing crowdsourcing research by suggesting the use of cognitive load assessments such as
    NASA Task Load Index surveys to evaluate workers pre and post--tasks
    \cite{embracingErrorKrishna,measuringCrowdsourcingCheng}.

    External management comes in other forms than scientific, as previously mentioned.
    Researchers in particular have noticed that their relationships with on--demand workers are%
,     at the least, complex.
    \citeauthor{storiesIraniSilberman} point out that their relationships with Turkers are highly complex;
    specifically, their interactions with field sites in which they work
    as designers and mediators of change influence the relationships they have with Turkers
    \cite{storiesIraniSilberman}.

    The scientific management of pieceworkers has been well--studied under the umbrella of assembly line research%
,     and even physiological study of pieceworkers closely resembles the
    research into cognitive loads and stress levels that we discussed among on--demand crowd workers
    \cite{hu1961parallel,pieceworkBiologicalHarm}.
    Even the complicated relationships between observers and workers themselves are not necessarily new;
    \citeauthor{riisOtherSideLives}'s photodocumentary of pieceworkers has even been re--examined through an exercise asking crowd workers
    to photograph themselves for similar purposes as \citeauthor{riisOtherSideLives}'s --- to document and humanize an otherwise abstracted, invisible workforce
    \cite{facesOfMechanicalTurk,turkopticon,riisOtherSideLives}.

@@

    \subsubsection{Resistance}
    It shouldn't surprise us, then, that workers have resisted the management imposed on them both by other people and their systems%
,     often without recourse or opportunity for feedback, let alone substantive input.
    Indeed, \citeauthor{uberAlgorithm} discover of Uber drivers that 
    many toggle their availability to avoid being dispatched to more distant locations%
,     resisting the intent of the designers of the systems and their ``algorithmic and data--driven management''
    \cite{uberAlgorithm}.

@@

    Resistance against managers in piecework and factory labor settings are deeply well--explored%
,     but perhaps the most relevant case study to draw on here is to be found in
    \citeauthor{waldinger1996helots}'s case study of ``Justice for Janitors''%
,     where marginalized workers managed to raise awareness for their plight and secure support for badly needed reforms
    \cite{waldinger1996helots}.
    The achievements of labor advocacy groups such as labor unions as resistant%
,     even adversarial organizations counter--balancing the management
    is somewhat well--understood
    \cite{russell1982collective,craig1992behavior}.
    We argue that these threads of resistance against management in various forms
    are in fact one.
  }
  % \theendnotes
  % \end{appendices}
